Obtaining free USArray data by multi-dimensional seismic reconstruction

### 2020-12-17 usarray/paper.tex
2020年12月16日 星期三 18时50分14秒 CST

The past two decades have witnessed a major proliferation of broadband seismic arrays around the globe.  One excellent example is USAarry, the seismology component of the national Earth science program EarthScope, that \dlo{had been migrating}\wen{migrated} continuously across the North American continent (year 2004-2013\wen{; now deployed in Alaska and northwestern Canada}), providing a dense sampling of the seismic wavefield beneath its footprint. The availability of a large amount \wen{of} high-quality \dlo{array }data offers unique opportunities for \dlo{conducting }high-resolution seismic imaging, which leads to \wen{a} \dlo{much improved}\wen{much-improved} understanding of \wen{the} Earth's structure at various scales \cite{van2005surface,moschetti2007surface,yang2008structure,lin2009eikonal,yuan2010lithospheric,sigloch2011mantle,porritt2014seismic,schaeffer2014imaging,schmandt2014p,bao2016imaging,burdick2017model}. The relatively even-spaced sensors, with an average spacing of $ \sim $70 km, form an ideal network configuration for \dlo{applying the} \wen{the application of} array-based \dlo{method}\wen{methods} \cite{rost2002array,gu2010arrays}. While the quantity of array data is continuously growing, \dlo{its quality is still limited}\wen{the improvement of data quality is hampered} by the presence of noise and a biased spatial sampling \dlo{resulting}\wen{that results} from \dlo{the }unevenly distributed earthquake sources and stations. Both factors (i.e., quantity and quality) play an important role in exploiting the \dlo{information from the }data and achieving robust imaging outputs. Most \dlo{resolution}\wen{data} improvement efforts have been focusing on increasing the data volume whereas generally less attention was paid to improve the quality of \dlo{the }existing \dlo{data}\wen{recordings}. The high-quality data with a regular spatial sampling can greatly benefit data analysis, processing and visualization, and also improve the numerical stability and accuracy for grid-based seismic imaging techniques (e.g., Eikonal \cite{lin2009eikonal} and Helmholtz tomography \cite{lin2011helmholtz}). As a result, \dlo{the }regularization approach\wen{es} that suppress\dlo{es} the noise and interpolate\dlo{s} the missing traces of array data \dlo{is}\wen{are} highly demanded \cite{mostafa2016geo,mostafa2016bssa,schneider2017improvement}.

\dlo{There are some}\wen{Some} effective methods for seismic data reconstruction \dlo{from}\wen{have been proposed in} the exploration seismology community. One type of the most widely used methods is based on \wen{a} sparse transform that maps the seismic signals to certain domains (e.g., Fourier \cite{abma2006}, curvelet \cite{yu2017mapping}, \wen{slant stacklet \cite{ventosa2015extraction}, }and seislet domains \cite{fomel2010seislet}), where the useful information can be sparsely represented and separated from the missing data and random noise. Another type of mainstream \wen{methods} is based on the Cadzow filtering or the Singular Spectrum Analysis (SSA) \cite{ssa}, which is a rank-reduction based method that transforms the data to frequency-wavenumber or frequency-space domains to extract the spatial coherency of the entire data set for reconstructing the missing information. Oropeza and Sacchi (2011) \cite{mssa} extended the SSA method to multi-channel version to tackle the 3-D seismic data reconstruction challenge and later on Kreimer et al. (2013) \cite{kreimer2013} formulated the high-dimensional reconstruction as a nuclear-norm constrained tensor completion problem in the frequency-space domain. More recently, Chen et al. (2016) \cite{yangkang2016irr5d} improved the traditional truncated singular value decomposition (TSVD) method by deriving a new rank-reduction formula\dlo{, which}\wen{ that} better decomposes the data space into signal and noise subspaces. All aforementioned reconstruction methods are commonly applied to seismic data from exploration-scale surveys, while their applications to earthquake data, especially the multidimensional data recorded by large-scale seismic \dlo{array}\wen{arrays}, have been seldom reported.

In global seismology community, several methods have been proposed to interpolate the irregularly sampled seismic data. Most earlier studies have been concentrating on interpolating the receiver functions \cite{langston1977effect} that consist of P to S converted waves based on a certain form of spatial smoothing \dlo{such as}\wen{, including, for example,} weighted stacking with either linear \cite{chengping2015}, gaussian \cite{neal1999imaging, song2017moho} or cubic spline functions \cite{sheldrake2002regional, zhang2014receiver}. Also implemented are methods based on high-resolution Radon transform \cite{wilson2007teleseismic}, \dlo{sigular}\wen{singular} spectrum analysis \cite{gu2015sharp, dokht2016singular} and, more recently, non-linear waveform stretching-and-squeezing \cite{hu2018wavefield}.  Aside from interpolating the receiver functions, Schneider et al. (2017) \cite{schneider2017improvement} reconstruct\wen{ed} the weak-amplitude under-side reflections from the mantle transition zone (i.e., PP precursors) while utilizing a compressive sensing based approach that seeks the sparsity of dominating \dlo{energies}\wen{energy} in the frequency-wavenumber domain.  A recent study also \dlo{applies}\wen{applied} the idea of compressive sensing to reconstruct the synthetic surface wavefields via a sparse representation using a plane wave basis \cite{zhan2018application}.  These earlier studies represent \dlo{continuous}\wen{continuing} efforts of the global seismology community in improving the earthquake data towards a regularly sampled wavefield\dlo{, yet}\wen{. However,} challenge still exists in view that 1) only a specific type of data (e.g, receiver functions, PP precursors), which is typically structurally simple, is reconstructed, and 2) the energy of useful signals tends \wen{to} be excessively smoothed by the ad hoc interpolation schemes, which limits the data resolution thereby the resolvability of small-scale structures.

@@

\section*{Results}
\subsection*{Synthetic test}
We first conduct a synthetic test to demonstrate the performance of the proposed methodology. The model is designed to honor  the complex Moho structure in central US \cite{schmandt2015distinct} that is characterized by \dlo{a large depth variation}\wen{large depth variations} by as much as 20 km (Figure \ref{fig:syn}).  The elastic properties (velocity and density) of the crust and upper mantle are obtained from the average values of AK135 continental model\cite{kennett1995constraints} (Figures 1a-1c).  We synthesize the recorded wavefield by solving the 3D elastic wave equation based on a finite-difference method\dlo{ with a GPU implementation}\old{ (see Supplementary material for mathematical detail)}. We simulate plane-wave incidence of teleseismic earthquake by simultaneously injecting energy from multiple point sources located on a plane in the upper mantle (Figure \ref{fig:obs}). %\wen{The direction of wavefront is determined from the epicenter distance and azimuth of the earthquake investigated in this study. The stacked P-wave of actual earthquake recordings is employed as the effective source-time function to ensure a similar frequency content and signal energy of the synthetics. The frequency band  of the synthetic data as revealed by the spectrum plots in the Supplementary material is 0-0.3 Hz.}
\wen{The physical parameters of an earthquake (e.g., epicenter and magnitude) are implicitly considered in our simulation. The direction of wavefront is determined from the epicenter distance and azimuth of the earthquake investigated in this study. The stacked P-wave of actual earthquake recordings is employed as the effective source-time function to honor the actual earthquake source parameters and ensure a similar frequency content and signal energy of the synthetics. }

The 3D seismic data consists of 200 time samples with a sampling rate of 0.5 sec and 100 equally spaced spatial samples in both longitudinal \new{(X) and  latitudinal (Y)} directions (Figure \ref{fig:syn-clean}).  The simulated wavefield shows clear P and Moho converted phases (Ps) (Figure \ref{fig:syn-clean}). To mimic the realistic signal-to-noise ratio (SNR), we add real noise that \dlo{proceeds}\wen{precedes} the first arrivals (i.e., P waves) from the USArray data to the synthetics (Figure \ref{fig:syn-noisy}). The missing traces are generated by applying the sampling matrix (Figure \ref{fig:syn-mask}) to the noisy data. The final simulated data contains 30\% missing traces (Figure \ref{fig:syn-obs}). To quantitatively evaluate the data quality, we use a SNR criterion defined as follows: $\text{SNR}=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \mathbf{s} -\hat{\mathbf{s}}\Arrowvert_2^2}$, where $\mathbf{s}$ denotes the exact solution (i.e., the clean data), and $\hat{\mathbf{s}}$ is the noise contaminated or incomplete data. The respective data quality \dlo{factors}\wen{metrics} (SNR) for the noisy and  incomplete data are \dlo{7.51}\wen{10.12} and \dlo{4.64}\wen{4.35} dB, suggesting a significantly decreased data quality caused by missing traces. \wen{This criterion is also applied to assess the quality of reconstruction, where $\hat{\mathbf{s}}$ represents the recovered data using the global or local reconstruction algorithms. Thus, the SNR measures the deviation of an estimated data from its true solution.}

%The maximum amplitude of the second event varies at different coordinates $(X,Y)$. We generate the second event by shifting a flat event according to the shift-time table, shown in Figures \ref{fig:syn_how}(a) and \ref{fig:syn_how}(b). The values in the shift-time table denote the corresponding time shifts of the second event in the synthetic data example. The amplitude variation of the second event is shown in Figures \ref{fig:syn_how}(c) and \ref{fig:syn_how}(d). The left column in Figure \ref{fig:syn_how} shows the ``SURF" plots while the right column in Figure \ref{fig:syn_how} shows the ``GREY" plots. ``SURF" and ``GREY" correspond to the two different plotting functions in the MATLAB software platform. From Figure \ref{fig:syn_how} we can see that the maximum and minimum time shifts differ by a bout 15 seconds. The curvature becomes the largest when the time shifts become largest or smallest. It is also clear that the amplitude of the second event decreases from about 1.5 at the four corners to about 0.6 in the center.  Figures \ref{fig:syn-rr} and \ref{fig:syn-rr-e} show the reconstructed data and its corresponding reconstruction error using the global rank-reduction method. Figures \ref{fig:syn-lrr} and \ref{fig:syn-lrr-e} plot the reconstructed data using the localized rank-reduction method and its corresponding reconstruction error.
The global rank-reduction method assumes that the seismic data are composed of several plane waves, \dlo{while}\wen{however,} this assumption is often violated due to the presence of  non-planar wavefield\wen{s} in realistic models (see Figure \ref{fig:syn}). Thus, we improve the global rank-reduction \dlo{based MSSA}\wen{method} using a localized scheme. This method divides the data cube into several smaller volumes to minimize the curvature of seismic waves, which essentially imposes a local plane-wave constraint to alleviate the non-planar effect\wen{s}.  More sophisticated methods based on non-plane-wave assumption\wen{s} (e.g.,  non-stationary principal component analysis \cite{zhao2016principal}) may offer better solutions to the curved wavefronts. To implement the localized rank-reduction method, we apply a 3D moving window with \wen{a} size of $50\times 50\times 50$ to the data volume. We \dlo{also }\dlo{allows}\wen{allow} \dlo{an}\wen{a} 25-points \wen{(i.e., 50\%)} overlap in each direction between successive windows to suppress the edge effects. For each subset of the data volume within the moving window, we use a \wen{reference} rank of three to \dlo{synthesize}\wen{compute} the trajectory matrix \wen{(see Methods)}, \dlo{whereas the rank used in the global rank-reduction method is nine.}\wen{whereas a reference value of nine is adopted in global rank-reduction method.}  In the global case, the two plane waves are well reconstructed (Figure \ref{fig:syn-rr}), but the curved wavefront exhibits significant reconstruction errors, particularly in \dlo{the }areas with large curvatures (Figure \ref{fig:syn-rr-e}). \dlo{On the other hand}\wen{In comparison}, the localized rank-reduction method does not cause obvious damages to the signal (Figure \ref{fig:syn-lrr}) and the reconstruction error is almost zero everywhere (Figure \ref{fig:syn-lrr-e}). Based on SNR metric, the respective quality \dlo{factors}\wen{metrics} for the global and localized reconstructions are \dlo{7.51 dB and 14.38 dB}\wen{17.34 dB and 21.53 dB}, suggesting a better performance of \dlo{localized reconstruction than the global algorithm}\wen{the latter approach}. We extract a single trace at \dlo{the}\wen{a} location where large curvature exists (Figure \ref{fig:syn-trace}). \dlo{It is clear that the}\wen{The} reconstructed trace using localized rank-reduction method (green) almost fully recovers the input (black; Figure \ref{fig:syn-ss-z}), whereas an obvious time shift is present in the trace obtained from the global method (blue; see Figure \ref{fig:syn-ss-z}).

We also use local similarity \cite{fomel2007localattr}, which measures the similarity between two signals in a local sense, to evaluate the reconstruction performance. A mathematical introduction of the local similarity metric is provided in the Supplementary \old{material}\new{Note 2}. In our case, we intend to obtain a reconstruction result that is as close to the clean data as possible.  The local similarity between the clean and the reconstructed data using the global rank-reduction method shows obvious low values along the curved wavefront (Figure \ref{fig:syn-rr-simi}). \dlo{The}\wen{In comparison, the} local similarity of localized reconstruction is high throughout the data volume regardless of the shape of the wavefront (Figure \ref{fig:syn-lrr-simi}). We \dlo{also}\wen{further} investigate the effects of sampling ratios (i.e., the percentage of missing data) on the reconstruction.  To this end, we vary the sampling ratios from 90\% to 10\% and randomly remove the traces. The test results show that 1) the reconstruction performance, \wen{which is defined as SNR using equation 8,} improves with an increasing sampling ratio, 2) the proposed algorithm is robust even at the low end \wen{(30-40\%)} of the sampling range, and 3) the localized rank-reduction implementation always achieves superior reconstruction performance than the global method \wen{(Figure \ref{fig:snr-n})}.

@@

@@

%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-vp}
%    \label{fig:syn-jw-vp}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-vs}
%    \label{fig:syn-jw-vs}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-rho}
%    \label{fig:syn-jw-rho}}\\
%    \subfigure[]{\includegraphics[width=0.6\textwidth]{Fig/observation}

@@

%	\caption{Wavefield simulation of plane-wave incidence beneath a regional array. The synthetic model is constructed using real Moho constraints\cite{schmandt2015distinct} and\dlo{ and} elastic parameters of (a) P-wave velocities, (b) S-wave velocities and (c) densities from a 1D reference model\cite{kennett1995constraints}. The blue lines mark the location of horizontal and vertical slices, where the values of model parameters are demonstrated and projected onto the corresponding sides of the model cube. (d) Observation system demonstrating the positions of planar source and receivers. The stars at the surface denote the evenly distributed receivers and symbols on the dipping plane denote the injected source positions. }
%	\label{fig:syn}

@@

%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-clean}
%    \label{fig:syn-clean}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-noisy}
%    \label{fig:syn-noisy}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-mask}
%    \label{fig:syn-mask}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-obs}
%    \label{fig:syn-obs}}

@@

%	\label{fig:syns}

@@

%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-rr}
%    \label{fig:syn-rr}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-lrr}
%    \label{fig:syn-lrr}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-rr-e}
%    \label{fig:syn-rr-e}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-jw-lrr-e}
%    \label{fig:syn-lrr-e}}

@@

%	\label{fig:syns-rn}

@@

%	\subfigure[]{\includegraphics[width=0.4\textwidth]{Fig/syn-jw-ss-0}
%    \label{fig:syn-ss-0}}
%    \subfigure[]{\includegraphics[width=0.4\textwidth]{Fig/syn-jw-ss-z}
%    \label{fig:syn-ss-z}}

>>>>

The past two decades have witnessed a major proliferation of broadband seismic arrays around the globe.  One excellent example is USAarry, the seismology component of the national Earth science program EarthScope, that \dlo{had been migrating}\wen{migrated} continuously across the North American continent (year 2004-2013\wen{; now deployed in Alaska and northwestern Canada}), providing a dense sampling of the seismic wavefield beneath its footprint. The availability of a large amount \wen{of} high-quality \dlo{array }data offers unique opportunities for \dlo{conducting }high-resolution seismic imaging, which leads to \wen{a} \dlo{much improved}\wen{much-improved} understanding of \wen{the} Earth's structure at various scales \cite[]{van2005surface,moschetti2007surface,yang2008structure,lin2009eikonal,yuan2010lithospheric,sigloch2011mantle,porritt2014seismic,schaeffer2014imaging,schmandt2014p,bao2016imaging,burdick2017model}. The relatively even-spaced sensors, with an average spacing of $ \sim $70 km, form an ideal network configuration for \dlo{applying the} \wen{the application of} array-based \dlo{method}\wen{methods} \cite[]{rost2002array,gu2010arrays}. While the quantity of array data is continuously growing, \dlo{its quality is still limited}\wen{the improvement of data quality is hampered} by the presence of noise and a biased spatial sampling \dlo{resulting}\wen{that results} from \dlo{the }unevenly distributed earthquake sources and stations. Both factors (i.e., quantity and quality) play an important role in exploiting the \dlo{information from the }data and achieving robust imaging outputs. Most \dlo{resolution}\wen{data} improvement efforts have been focusing on increasing the data volume whereas generally less attention was paid to improve the quality of \dlo{the }existing \dlo{data}\wen{recordings}. The high-quality data with a regular spatial sampling can greatly benefit data analysis, processing and visualization, and also improve the numerical stability and accuracy for grid-based seismic imaging techniques (e.g., Eikonal \cite[]{lin2009eikonal} and Helmholtz tomography \cite[]{lin2011helmholtz}). As a result, \dlo{the }regularization approach\wen{es} that suppress\dlo{es} the noise and interpolate\dlo{s} the missing traces of array data \dlo{is}\wen{are} highly demanded \cite[]{mostafa2016geo,mostafa2016bssa,schneider2017improvement}.

\dlo{There are some}\wen{Some} effective methods for seismic data reconstruction \dlo{from}\wen{have been proposed in} the exploration seismology community. One type of the most widely used methods is based on \wen{a} sparse transform that maps the seismic signals to certain domains (e.g., Fourier \cite[]{abma2006}, curvelet \cite[]{yu2017mapping}, \wen{slant stacklet \cite[]{ventosa2015extraction}, }and seislet domains \cite[]{fomel2010seislet}), where the useful information can be sparsely represented and separated from the missing data and random noise. Another type of mainstream \wen{methods} is based on the Cadzow filtering or the Singular Spectrum Analysis (SSA) \cite[]{ssa}, which is a rank-reduction based method that transforms the data to frequency-wavenumber or frequency-space domains to extract the spatial coherency of the entire data set for reconstructing the missing information. Oropeza and Sacchi (2011) \cite[]{mssa} extended the SSA method to multi-channel version to tackle the 3-D seismic data reconstruction challenge and later on Kreimer et al. (2013) \cite[]{kreimer2013} formulated the high-dimensional reconstruction as a nuclear-norm constrained tensor completion problem in the frequency-space domain. More recently, Chen et al. (2016) \cite[]{yangkang2016irr5d} improved the traditional truncated singular value decomposition (TSVD) method by deriving a new rank-reduction formula\dlo{, which}\wen{ that} better decomposes the data space into signal and noise subspaces. All aforementioned reconstruction methods are commonly applied to seismic data from exploration-scale surveys, while their applications to earthquake data, especially the multidimensional data recorded by large-scale seismic \dlo{array}\wen{arrays}, have been seldom reported.

In global seismology community, several methods have been proposed to interpolate the irregularly sampled seismic data. Most earlier studies have been concentrating on interpolating the receiver functions \cite[]{langston1977effect} that consist of P to S converted waves based on a certain form of spatial smoothing \dlo{such as}\wen{, including, for example,} weighted stacking with either linear \cite[]{chengping2015}, gaussian \cite[]{neal1999imaging, song2017moho} or cubic spline functions \cite[]{sheldrake2002regional, zhang2014receiver}. Also implemented are methods based on high-resolution Radon transform \cite[]{wilson2007teleseismic}, \dlo{sigular}\wen{singular} spectrum analysis \cite[]{gu2015sharp, dokht2016singular} and, more recently, non-linear waveform stretching-and-squeezing \cite[]{hu2018wavefield}.  Aside from interpolating the receiver functions, Schneider et al. (2017) \cite[]{schneider2017improvement} reconstruct\wen{ed} the weak-amplitude under-side reflections from the mantle transition zone (i.e., PP precursors) while utilizing a compressive sensing based approach that seeks the sparsity of dominating \dlo{energies}\wen{energy} in the frequency-wavenumber domain.  A recent study also \dlo{applies}\wen{applied} the idea of compressive sensing to reconstruct the synthetic surface wavefields via a sparse representation using a plane wave basis \cite[]{zhan2018application}.  These earlier studies represent \dlo{continuous}\wen{continuing} efforts of the global seismology community in improving the earthquake data towards a regularly sampled wavefield\dlo{, yet}\wen{. However,} challenge still exists in view that 1) only a specific type of data (e.g, receiver functions, PP precursors), which is typically structurally simple, is reconstructed, and 2) the energy of useful signals tends \wen{to} be excessively smoothed by the ad hoc interpolation schemes, which limits the data resolution thereby the resolvability of small-scale structures.

@@

\section*{Results}
\subsection*{Synthetic test}
We first conduct a synthetic test to demonstrate the performance of the proposed methodology. The model is designed to honor  the complex Moho structure in central US \cite[]{schmandt2015distinct} that is characterized by \dlo{a large depth variation}\wen{large depth variations} by as much as 20 km (Figure \ref{fig:syn-us-vp,syn-us-vs,syn-us-rho,obs}).  The elastic properties (velocity and density) of the crust and upper mantle are obtained from the average values of AK135 continental model\cite[]{kennett1995constraints} (Figures 1a-1c).  We synthesize the recorded wavefield by solving the 3D elastic wave equation based on a finite-difference method\dlo{ with a GPU implementation}\old{ (see Supplementary material for mathematical detail)}. We simulate plane-wave incidence of teleseismic earthquake by simultaneously injecting energy from multiple point sources located on a plane in the upper mantle (Figure \ref{fig:obs}). %\wen{The direction of wavefront is determined from the epicenter distance and azimuth of the earthquake investigated in this study. The stacked P-wave of actual earthquake recordings is employed as the effective source-time function to ensure a similar frequency content and signal energy of the synthetics. The frequency band  of the synthetic data as revealed by the spectrum plots in the Supplementary material is 0-0.3 Hz.}
\wen{The physical parameters of an earthquake (e.g., epicenter and magnitude) are implicitly considered in our simulation. The direction of wavefront is determined from the epicenter distance and azimuth of the earthquake investigated in this study. The stacked P-wave of actual earthquake recordings is employed as the effective source-time function to honor the actual earthquake source parameters and ensure a similar frequency content and signal energy of the synthetics. }

The 3D seismic data consists of 200 time samples with a sampling rate of 0.5 sec and 100 equally spaced spatial samples in both longitudinal \new{(X) and  latitudinal (Y)} directions (Figure \ref{fig:syn-us-clean}).  The simulated wavefield shows clear P and Moho converted phases (Ps) (Figure \ref{fig:syn-us-clean}). To mimic the realistic signal-to-noise ratio (SNR), we add real noise that \dlo{proceeds}\wen{precedes} the first arrivals (i.e., P waves) from the USArray data to the synthetics (Figure \ref{fig:syn-us-noisy}). The missing traces are generated by applying the sampling matrix (Figure \ref{fig:syn-us-mask}) to the noisy data. The final simulated data contains 30\% missing traces (Figure \ref{fig:syn-us-obs}). To quantitatively evaluate the data quality, we use a SNR criterion defined as follows: $\text{SNR}=10\log_{10}\frac{\Arrowvert \mathbf{s} \Arrowvert_2^2}{\Arrowvert \mathbf{s} -\hat{\mathbf{s}}\Arrowvert_2^2}$, where $\mathbf{s}$ denotes the exact solution (i.e., the clean data), and $\hat{\mathbf{s}}$ is the noise contaminated or incomplete data. The respective data quality \dlo{factors}\wen{metrics} (SNR) for the noisy and  incomplete data are \dlo{7.51}\wen{10.12} and \dlo{4.64}\wen{4.35} dB, suggesting a significantly decreased data quality caused by missing traces. \wen{This criterion is also applied to assess the quality of reconstruction, where $\hat{\mathbf{s}}$ represents the recovered data using the global or local reconstruction algorithms. Thus, the SNR measures the deviation of an estimated data from its true solution.}

%The maximum amplitude of the second event varies at different coordinates $(X,Y)$. We generate the second event by shifting a flat event according to the shift-time table, shown in Figures \ref{fig:syn_how}(a) and \ref{fig:syn_how}(b). The values in the shift-time table denote the corresponding time shifts of the second event in the synthetic data example. The amplitude variation of the second event is shown in Figures \ref{fig:syn_how}(c) and \ref{fig:syn_how}(d). The left column in Figure \ref{fig:syn_how} shows the ``SURF" plots while the right column in Figure \ref{fig:syn_how} shows the ``GREY" plots. ``SURF" and ``GREY" correspond to the two different plotting functions in the MATLAB software platform. From Figure \ref{fig:syn_how} we can see that the maximum and minimum time shifts differ by a bout 15 seconds. The curvature becomes the largest when the time shifts become largest or smallest. It is also clear that the amplitude of the second event decreases from about 1.5 at the four corners to about 0.6 in the center.  Figures \ref{fig:syn-us-rr} and \ref{fig:syn-us-rr-e} show the reconstructed data and its corresponding reconstruction error using the global rank-reduction method. Figures \ref{fig:syn-us-lrr} and \ref{fig:syn-us-lrr-e} plot the reconstructed data using the localized rank-reduction method and its corresponding reconstruction error.
The global rank-reduction method assumes that the seismic data are composed of several plane waves, \dlo{while}\wen{however,} this assumption is often violated due to the presence of  non-planar wavefield\wen{s} in realistic models (see Figure \ref{fig:syn-us-vp,syn-us-vs,syn-us-rho,obs}). Thus, we improve the global rank-reduction \dlo{based MSSA}\wen{method} using a localized scheme. This method divides the data cube into several smaller volumes to minimize the curvature of seismic waves, which essentially imposes a local plane-wave constraint to alleviate the non-planar effect\wen{s}.  More sophisticated methods based on non-plane-wave assumption\wen{s} (e.g.,  non-stationary principal component analysis \cite[]{zhao2016principal}) may offer better solutions to the curved wavefronts. To implement the localized rank-reduction method, we apply a 3D moving window with \wen{a} size of $50\times 50\times 50$ to the data volume. We \dlo{also }\dlo{allows}\wen{allow} \dlo{an}\wen{a} 25-points \wen{(i.e., 50\%)} overlap in each direction between successive windows to suppress the edge effects. For each subset of the data volume within the moving window, we use a \wen{reference} rank of three to \dlo{synthesize}\wen{compute} the trajectory matrix \wen{(see Methods)}, \dlo{whereas the rank used in the global rank-reduction method is nine.}\wen{whereas a reference value of nine is adopted in global rank-reduction method.}  In the global case, the two plane waves are well reconstructed (Figure \ref{fig:syn-us-rr}), but the curved wavefront exhibits significant reconstruction errors, particularly in \dlo{the }areas with large curvatures (Figure \ref{fig:syn-us-rr-e}). \dlo{On the other hand}\wen{In comparison}, the localized rank-reduction method does not cause obvious damages to the signal (Figure \ref{fig:syn-us-lrr}) and the reconstruction error is almost zero everywhere (Figure \ref{fig:syn-us-lrr-e}). Based on SNR metric, the respective quality \dlo{factors}\wen{metrics} for the global and localized reconstructions are \dlo{7.51 dB and 14.38 dB}\wen{17.34 dB and 21.53 dB}, suggesting a better performance of \dlo{localized reconstruction than the global algorithm}\wen{the latter approach}. We extract a single trace at \dlo{the}\wen{a} location where large curvature exists (Figure \ref{fig:syn-us-ss-0,syn-us-ss-z}). \dlo{It is clear that the}\wen{The} reconstructed trace using localized rank-reduction method (green) almost fully recovers the input (black; Figure \ref{fig:syn-us-ss-z}), whereas an obvious time shift is present in the trace obtained from the global method (blue; see Figure \ref{fig:syn-us-ss-z}).

We also use local similarity \cite[]{fomel2007localattr}, which measures the similarity between two signals in a local sense, to evaluate the reconstruction performance. A mathematical introduction of the local similarity metric is provided in the Supplementary \old{material}\new{Note 2}. In our case, we intend to obtain a reconstruction result that is as close to the clean data as possible.  The local similarity between the clean and the reconstructed data using the global rank-reduction method shows obvious low values along the curved wavefront (Figure \ref{fig:syn-us-rr-simi}). \dlo{The}\wen{In comparison, the} local similarity of localized reconstruction is high throughout the data volume regardless of the shape of the wavefront (Figure \ref{fig:syn-us-lrr-simi}). We \dlo{also}\wen{further} investigate the effects of sampling ratios (i.e., the percentage of missing data) on the reconstruction.  To this end, we vary the sampling ratios from 90\% to 10\% and randomly remove the traces. The test results show that 1) the reconstruction performance, \wen{which is defined as SNR using equation 8,} improves with an increasing sampling ratio, 2) the proposed algorithm is robust even at the low end \wen{(30-40\%)} of the sampling range, and 3) the localized rank-reduction implementation always achieves superior reconstruction performance than the global method \wen{(Figure \ref{fig:snr-n})}.

@@

\multiplot{4}{syn-us-vp,syn-us-vs,syn-us-rho,obs}{width=0.4\textwidth}{Wavefield simulation of plane-wave incidence beneath a regional array. The synthetic model is constructed using real Moho constraints and\dlo{ and} elastic parameters of (a) P-wave velocities, (b) S-wave velocities and (c) densities from a 1D reference model. The blue lines mark the location of horizontal and vertical slices, where the values of model parameters are demonstrated and projected onto the corresponding sides of the model cube. (d) Observation system demonstrating the positions of planar source and receivers. The stars at the surface denote the evenly distributed receivers and symbols on the dipping plane denote the injected source positions.  }

\inputdir{syn}
\multiplot{4}{syn-us-clean,syn-us-noisy,syn-us-mask,syn-us-obs}{width=0.4\textwidth}{The \dlo{input synthetic}\wen{synthesized} data. (a) The clean data \dlo{containing two main seismic phases. The colors at zero time slice indicate the relative time perturbations of the second phase arrivals.  The cross-hair marks the location of the sample trace shown in Figure 6.}\wen{obtained from elastic wave simulation.} (b) The noisy data with \old{SNR=}\new{signal-to-noise ratio equals to} 10.12 dB. (c) The sampling matrix with a sampling ratio of \dlo{80}\wen{70}\% (d) The final data after applying the sampling matrix to noisy data in (b). The SNR of the \wen{input} data is \dlo{4.64}\wen{4.35} dB.}

\multiplot{4}{syn-us-rr,syn-us-lrr,syn-us-rr-e,syn-us-lrr-e}{width=0.4\textwidth}{Synthetic test results. (a) Reconstructed data using the global rank-reduction method.  The \old{SNR}\new{signal-to-noise ratio} of the reconstructed data is 17.34 dB. (b) Reconstructed data using the localized rank-reduction method (\old{SNR=}\new{signal-to-noise ratio is }21.53 dB). (c) and (d) Reconstruction errors corresponding to (a) and (b).}

\multiplot{2}{syn-us-ss-0,syn-us-ss-z}{width=0.4\textwidth}{Comparison of the single trace amplitude (X=225,Y=225) in \new{different scales.}\old{ (a) original and (b) zoomed-in scales .} \new{(a) Comparison in the original scale. (b) Comparison in the zoomed-in scale.} The black and pink lines represent \dlo{the }clean and noisy data, respectively. The trace processed using global and localized rank-reduction methods are shown by the blue and green lines, respectively. The black line (localized reconstruction) is almost completely overlapped with the green line (true solution), indicating that the error of reconstruction is \dlo{very small}\wen{minimal} for the proposed approach.}

\multiplot{2}{syn-us-rr-simi,syn-us-lrr-simi}{width=0.4\textwidth}{\old{Reconstruction performance comparison between (a) global and (b) localized rank-reduction methods using local similarity matrix.}\new{A comparison of reconstruction performance in terms of local similarity metric. (a) Local similarity using the global rank-reduction method. (b) Local similarity using the localized rank-reduction method.} Note that local similarity around curved wavefronts is noticeably lower in the global reconstruction results.}

\plot{snr-n}{width=\textwidth}{Reconstruction results at different sampling ratios. The reconstruction performance (SNR) improves with the increasing sampling ratio. The localized rank-reduction method always outperforms the global algorithm.}
\inputdir{./}

@@

%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-vp}
%    \label{fig:syn-us-vp}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-vs}
%    \label{fig:syn-us-vs}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-rho}
%    \label{fig:syn-us-rho}}\\
%    \subfigure[]{\includegraphics[width=0.6\textwidth]{Fig/obs}

@@

%	\caption{Wavefield simulation of plane-wave incidence beneath a regional array. The synthetic model is constructed using real Moho constraints\cite[]{schmandt2015distinct} and\dlo{ and} elastic parameters of (a) P-wave velocities, (b) S-wave velocities and (c) densities from a 1D reference model\cite[]{kennett1995constraints}. The blue lines mark the location of horizontal and vertical slices, where the values of model parameters are demonstrated and projected onto the corresponding sides of the model cube. (d) Observation system demonstrating the positions of planar source and receivers. The stars at the surface denote the evenly distributed receivers and symbols on the dipping plane denote the injected source positions. }
%	\label{fig:syn-us-vp,syn-us-vs,syn-us-rho,obs}

@@

%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-clean}
%    \label{fig:syn-us-clean}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-noisy}
%    \label{fig:syn-us-noisy}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-mask}
%    \label{fig:syn-us-mask}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-obs}
%    \label{fig:syn-us-obs}}

@@

%	\label{fig:syn-clean,syn-noisy,syn-mask,syn-obs}

@@

%	\subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-rr}
%    \label{fig:syn-us-rr}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-lrr}
%    \label{fig:syn-us-lrr}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-rr-e}
%    \label{fig:syn-us-rr-e}}
%    \subfigure[]{\includegraphics[width=0.22\textwidth]{Fig/syn-us-lrr-e}
%    \label{fig:syn-us-lrr-e}}

@@

%	\label{fig:syn-rr,syn-lrr,syn-rr-e,syn-lrr-e}

@@

%	\subfigure[]{\includegraphics[width=0.4\textwidth]{Fig/syn-us-ss-0}
%    \label{fig:syn-us-ss-0}}
%    \subfigure[]{\includegraphics[width=0.4\textwidth]{Fig/syn-us-ss-z}
%    \label{fig:syn-us-ss-z}}
